A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Unvague the speed claim.

Figure~\ref{fig:speed} compares the sentence encoding speed of the three models on random input data. We observe a substantial difference in runtime between the CPU and thin-stack implementations that increases with batch size. At the larger batch sizes that are most effective for test-time applications (e.g., 512+ examples), our model is 10--25x faster than the standard CPU implementation, and about 4x slower than the RNN baseline.

>>>>

Figure~\ref{fig:speed} compares the sentence encoding speed of the three models on random input data. We observe a substantial difference in runtime between the CPU and thin-stack implementations that increases with batch size. With a large but practical batch size of 512, the largest we on which we tested the TreeRNN, our model is about 25x faster than the standard CPU implementation, and about 4x slower than the RNN baseline.
